---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE,fig.width = 6, fig.height = 4)
library(tidyverse)
library(magick)
```



```{css}
body {
    color:  #0B5345    ;
    background-color: #EAF2F8       ;
    font-family:'Georgia',cursive;
}
h1 {
  color: #0B5345    ;
  background-color: white;
  padding: 20px;
  font-weight : bold

}
h2 {
  color:#0B5345    ;
  background-color: white;
  font-weight : bold;
}



```


## Effect of Temperature and Weather Types on the Visibility

- This report examines how different factors affect **Visibility**. such as :
  - Temperature
  - Weather Type
  
  
  
  
- My survey focused on collecting data from **Daily Weather Observations**, including:
  1. Temperature
  2. Humidity
  3. Wind Speed
  4. Weather Type
  5. Visibility


I have created *2 Bar Charts* to show the relationship between **Temperature**, **Weather Type** on **Visibility**




```{r}

#loading data from csv url

csv_file <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vQDOfFFR4SL_dCeIpvr_rrdFjkmHGmVdblsf9baVI_DRPOfmDMr2zr6fH2eVAh3ju9UBdk0q093f-HR/pub?gid=1796296273&single=true&output=csv"
logged_data <- read_csv(csv_file) 



#renaming columns for easy references

latest_data <- logged_data %>%
  rename(Temperature = 'What is the temperature (In Celcius) this time?',
    Weather = 'What is the general weather condition?',
    Humidity = 'What is the humidity (in %)?',
    Wind_Speed = 'What is the Wind Speed (km/h) ?',
    Visibility = 'What is the Visibility?')



```


```{r}
#Calculating min temp
minimum_temp <- min(latest_data$Temperature, na.rm =TRUE)


#Calculating max temp
maximum_temp <- max(latest_data$Temperature, na.rm =TRUE) 


#Calculating Mean Temp and round it to 1 decimal place
mean_temp <- mean(latest_data$Temperature, na.rm=TRUE) %>% round(1)



#Total number of observations of Temperature
length_temp <- length(latest_data$Temperature)



```
According to Summary Values of **Temperature**;

The **mean temperature** recorded was **`r mean_temp`**째C. 

The **maximum temperature** was **`r maximum_temp`**째C, while the **minimum temperature** was **`r minimum_temp`**째C.

The total number of recorded observations for temperature is **`r length_temp`**.



```{r}

#Total number of observations of Visibility as it is categorical only length used.
length_Visibility <-  length(latest_data$Visibility)

paste('The dataset contains',  length_Visibility , 'recorded observations of visibility', '.')

```


```{r fig.width = 8, fig.height = 4}



#BAR CHART (i) : Comparing Temperature and Visibility
#Create a plot Temperature of the first 10 rows of Temperature in latest_data using the x-axis for the Temperature. 
#And fill the color of each bar using the Visibility.
#using labs to add titles , x and y axis

latest_data %>%
  ggplot() +
  geom_bar(aes( x= Temperature,fill= Visibility)) +
  labs(title ="How the Temperature Affects What We See!", 
       subtitle = "Comparing Temperature and Visibility",
       x = 'Temperature (째C)',
       y= 'Number_of_observations',
caption = "Source: Weather survey")






#BAR CHART (ii): 
#We can see How each Weather Types affects the visibility by creating a bar chart

latest_data %>%
  ggplot() +
  geom_bar(aes( x= Weather,fill= Visibility)) +
  labs(title ="How the Visibility Changes according to the type of Weather!", 
       subtitle = "Comparing Weather types and Visibility",
       x = 'Weather Type',
       y= 'Number_of_observations',
caption = "Source: Weather survey")

```


The **Bar chart (i)** shows how Temperature affects Visibility while **Bar chart (ii)** explains how Visibility changes depending on each type of Weather. 


According to **Bar chart (i)** we can see ;
when the *temperature is higher* the visbility is **very clear** except for just 3 observations.
When the *temperature is lower* there is a high possibility of having **foggy and very foggy conditions**.


According to **Bar chart (ii)** we can see;
*Sunny conditions* have linked with the **higher visibility**.
During *cloudy conditions* it is more likely to be **very foggy and foggy**
*Rainy conditions* have mostly been recorded as **foggy**.




Additionally I have created a animation meme using **magick package** and it is about how the weather affects the mood which making the report more engaging.




```{r}
sun <- image_read('https://cdn.pixabay.com/photo/2016/11/26/20/26/ocean-1861597_1280.jpg') %>% 
  image_scale(500)

#top right with first text
sunny_txt <- image_blank (width = 500 ,
                     height = 700, 
                     color = 'white') %>%
  
  image_annotate (text = 'Wohoo\nSUMMER\nAND SUN! ',
                  gravity = 'center', 
                  size = 60 , 
                  color = '#F4D03F', 
                  font = 'Georgia')


#bottom left with second image
rain <- image_read('https://cdn.pixabay.com/photo/2023/01/13/18/58/gray-heron-7716748_1280.jpg') %>% image_scale(500)

#bottom right with second text
rainy_text <- image_blank (width = 500 , 
                    height = 750, 
                    color = '#96ADCB') %>%
  
  image_annotate (text = 'Not the\n rain again',
                  gravity = 'center', 
                  size = 60 , 
                  color = '#000000',
                  font = 'Georgia')


#first row of meme combined
first <- c(sun, sunny_txt) %>%
  image_append()

#second row of meme combined
second <- c(rain, rainy_text) %>%
  image_append()


animation <- c(first, second) %>% 
  image_animate(fps=1)

animation

#saving animation
image_write(animation,'my_animated_weather_meme.gif')


```
